Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-21 vesicle_code/docs/adhesion/revisions/reviewer1.tex
yny revisions july 21

\noindent
\item\comment{There was not enough physical insights on the vesicle
  alignment in extensional flow as presented in section IV. If the
  vesicles are placed centrally, what causes the pair to become
  asymmetric in the first place, since all components in the model are
  deterministic? The authors used vorticity contours, but the external
  flow is irrotational; so what is the origin of vorticity, and is it
  appropriate to use vorticity to explain the behavior?}
\begin{itemize}
  \item We have reorganized section IV based on the referee's feedback.
    To investigate the vesicle hydrodynamics in a planar extensional
    flow, we conducted new simulations where a left vesicle is placed at
    the stagnation point and the right vesicle is moving towards it.
    Depending on the initial elevation of the right vesicle off the
    $x$-axis, the vesicle hydrodynamics is different and we find
    configurations that are similar to those that we observe in the
    fluid trap. The simulation data shows that the membrane tension is
    highly non-uniform, and we speculate that the Marangoni stress
    contributes to asymmetric configuration of vesicles around the
    stagnation point, as for a single surfactant-laden drop in an
    extensional flow.

>>>>

\noindent
\item\comment{There was not enough physical insights on the vesicle
  alignment in extensional flow as presented in section IV. If the
  vesicles are placed centrally, what causes the pair to become
  asymmetric in the first place, since all components in the model are
  deterministic? The authors used vorticity contours, but the external
  flow is irrotational; so what is the origin of vorticity, and is it
  appropriate to use vorticity to explain the behavior?}
\begin{itemize}
  \item We agree with the referee that the external flow is irrotational without the
    vesicles. But once the vesicles are in the flow, the velocity field around the boundaries
    is altered by the drop deformation and balance of stress on the boundary. 
    For a viscous drop in an extensional flow a systematic way to compute some 
    flow perturbation due to a deformable drop can be found in {\it Advanced Transport Phenomena} 
    by L. Gary Leal, Cambridge University Press.

    To enhance clarity we have reorganized section IV based on the referee's feedback.
    To investigate the vesicle hydrodynamics in a planar extensional
    flow, we conducted new simulations where a left vesicle is placed at
    the stagnation point and the right vesicle is moving towards it.
    Depending on the initial elevation of the right vesicle off the
    $x$-axis, the vesicle hydrodynamics is different and we find
    configurations that are similar to those that we observe in the
    fluid trap. The simulation data shows that the membrane tension is
    highly non-uniform, and we speculate that the Marangoni stress
    contributes to asymmetric configuration of vesicles around the
    stagnation point, as in the case for a single surfactant-laden drop in an
    extensional flow.
